% !TeX root = ../main.tex
\chapter*{REFERENCES}
\addcontentsline{toc}{chapter}{REFERENCES}

\begin{enumerate}

\item
M. Fateh, T. T. T. Nguyen, S. George, and H. Hacid.
\textbf{Source type:} Journal article / cybersecurity education research.
\textit{Leveraging LLMs for generation and evaluation of cybersecurity training scenarios: a case study of phishing attack simulations},
International Journal of Information Security, 2025.
Available: \url{https://link.springer.com/article/10.1007/s44427-025-00006-3}.

\item
J. Molina, T. Stengel, and S. Eickhoff.
\textbf{Source type:} Preprint / LLM security analysis research.
\textit{Prompt Injection Detection with Hidden-Markov Models},
arXiv preprint, 2024.
Available: \url{https://arxiv.org/abs/2412.01421}.

\item
P. M. Nell, A. M. Trindade, C. M. Junqueira, A. C. B. Garcia, and C. M. N. dos Santos.
\textbf{Source type:} Preprint / RAG evaluation research.
\textit{ERA: Evaluating RAG with LLMs as Judges in Incident Postmortems},
arXiv preprint, 2026.
Available: \url{https://arxiv.org/abs/2604.20854}.

\item
J. Hu, X. Wen, and L. Wang.
\textbf{Source type:} Preprint / adversarial testing of LLM agents.
\textit{R-Bench: Benchmarking and Enhancing Robustness in LLM-Based Multi-Agent Systems},
arXiv preprint, 2026.
Available: \url{https://arxiv.org/abs/2604.20598}.

\item
R. Prabhakar, R. Tanna, and A. N. Srivastava.
\textbf{Source type:} Preprint / cyber threat intelligence with retrieval research.
\textit{RARE: Retrieval-Augmented Reasoning and Extraction for Cyber Threat Intelligence from IOC Reports},
arXiv preprint, 2026.
Available: \url{https://arxiv.org/abs/2604.19047}.

\item
V. Mazzi, I. Gandin, M. Pavan, and F. Silvestri.
\textbf{Source type:} Preprint / context-aware retrieval research.
\textit{Context-Aware Search on Documentation Graphs for Enhanced Code Generation},
arXiv preprint, 2026.
Available: \url{https://arxiv.org/abs/2604.18424}.

\item
S. Li, Z. Huang, Y. Zhang, Z. Tan, W. Liang, and D. Tao.
\textbf{Source type:} Preprint / reasoning benchmark research.
\textit{Evaluating Multi-Hop Reasoning in Large Language Models via Open-Domain Information-Seeking Questions},
arXiv preprint, 2026.
Available: \url{https://arxiv.org/abs/2604.18234}.

\item
OWASP Foundation.
\textbf{Source type:} Security standard / industry guidance.
\textit{OWASP Top 10: The Ten Most Critical Web Application Security Risks},
2021.
Available: \url{https://owasp.org/Top10/}.

\item
National Institute of Standards and Technology (NIST).
\textbf{Source type:} Government standard / technical guideline.
\textit{Security and Privacy Controls for Information Systems and Organizations (SP 800-53 Rev. 5)},
2020.
Available: \url{https://csrc.nist.gov/pubs/sp/800/53/r5/final}.

\item
MITRE.
\textbf{Source type:} Threat intelligence knowledge base / framework documentation.
\textit{MITRE ATT\&CK Framework},
Available: \url{https://attack.mitre.org/}.

\item
Proxmox Server Solutions GmbH.
\textbf{Source type:} Virtualization platform documentation.
\textit{Proxmox Virtual Environment Documentation},
Available: \url{https://pve.proxmox.com/pve-docs/}.

\item
Wazuh Inc.
\textbf{Source type:} SIEM platform documentation.
\textit{Wazuh Documentation},
Available: \url{https://documentation.wazuh.com/}.

\item
Docker Inc.
\textbf{Source type:} Container platform documentation.
\textit{Docker Documentation},
Available: \url{https://docs.docker.com/}.

\item
HashiCorp.
\textbf{Source type:} Infrastructure automation documentation.
\textit{Packer Documentation},
Available: \url{https://developer.hashicorp.com/packer/docs}.

\item
Ansible Project.
\textbf{Source type:} Automation framework documentation.
\textit{Ansible Documentation},
Available: \url{https://docs.ansible.com/}.

\item
FastAPI.
\textbf{Source type:} Backend framework documentation.
\textit{FastAPI Documentation},
Available: \url{https://fastapi.tiangolo.com/}.

\item
LangChain Inc.
\textbf{Source type:} LLM orchestration framework documentation.
\textit{LangGraph Documentation},
Available: \url{https://langchain-ai.github.io/langgraph/}.

\item
Qdrant.
\textbf{Source type:} Vector database documentation.
\textit{Qdrant Documentation},
Available: \url{https://qdrant.tech/documentation/}.

\item
VMware, Inc.
\textbf{Source type:} Message broker documentation.
\textit{RabbitMQ Documentation},
Available: \url{https://www.rabbitmq.com/docs}.

\item
Celery Project.
\textbf{Source type:} Distributed task queue documentation.
\textit{Celery Documentation},
Available: \url{https://docs.celeryq.dev/}.

\item
Redis Ltd.
\textbf{Source type:} In-memory data store documentation.
\textit{Redis Documentation},
Available: \url{https://redis.io/docs/}.

\item
The PostgreSQL Global Development Group.
\textbf{Source type:} Relational database documentation.
\textit{PostgreSQL Documentation},
Available: \url{https://www.postgresql.org/docs/}.

\item
Traefik Labs.
\textbf{Source type:} Reverse proxy documentation.
\textit{Traefik Proxy Documentation},
Available: \url{https://doc.traefik.io/traefik/}.

\item
Apache Software Foundation.
\textbf{Source type:} Remote access gateway documentation.
\textit{Apache Guacamole Documentation}.
Available: \url{https://guacamole.apache.org/doc/}.

\item
F5, Inc.
\textbf{Source type:} Web server / reverse proxy documentation.
\textit{NGINX Documentation},
Available: \url{https://docs.nginx.com/}.

\item
OWASP Foundation.
\textbf{Source type:} Web application firewall ruleset documentation.
\textit{ModSecurity Core Rule Set (CRS) Documentation},
Available: \url{https://coreruleset.org/docs/}.

\item
Google.
\textbf{Source type:} API documentation / LLM service documentation.
\textit{Gemini API Documentation},
Available: \url{https://ai.google.dev/gemini-api/docs}.

\end{enumerate}